Rectangulotopes

### 2024-04-21 draft/rectangulotopes.tex
typo
minor changes

\begin{figure}
	\capstart
	\centerline{\includegraphics[scale=.6]{permutahedronLeft4} \qquad \raisebox{-.4cm}{\includegraphics[scale=.6]{associahedron4}}}
	\caption{The permutahedron~$\Perm(4)$ (left) and the associahedron~$\Asso(4)$ (right). \cite[Fig.~1]{MR3964495} \&~\cite[Fig.~5]{MR4584712}}
	\label{fig:quotientopes}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=.7\textwidth]{rectangulations.pdf}
	\caption{Three rectangulations. All three rectangulations are weakly equivalent, but only the first two are strongly equivalent. Only the third one is diagonal.}
	\label{fig:rectequiv}
\end{figure}

@@

@@

\begin{figure}
	\centerline{\includegraphics[width=.5\textwidth]{strongRectangulation} \qquad \includegraphics[width=.5\textwidth]{strongRectangulationTrees}}
	\caption{A rectangulation $R$ (left) and its pair of binary trees $S(R)$ and $T(R)$ (right). Example from \cite{ACFF24}.}
        % The corresponding $2$-clumped permutation is $[7,5,14,8,1,6,15,11,4,10,16,2,9,13,3,12]$ and its inverse is $[5, 12, 15, 9, 2, 6, 1, 4, 13, 10, 8, 16, 14, 3, 7, 11]$.
        \label{fig:strongRectangulation}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=.5\textwidth]{weakRectangulation} \qquad \includegraphics[width=.5\textwidth]{weakRectangulationTrees}}
	\caption{A diagonal rectangulation (left) and its pair of twin binary trees (right). Example from \cite{ACFF24}.}
	% The corresponding twisted Baxter permutation is $[7, 5, 1, 14, 8, 6, 4, 2, 11, 10, 9, 3, 15, 16, 13, 12]$ and its inverse is $[3, 8, 12, 7, 2, 6, 1, 5, 11, 10, 9, 16, 15, 4, 13, 14]$.
	\label{fig:weakRectangulation}
\end{figure}

Fix a rectangulation~$R$ of size~$n$, and consider the directed graph~$D(R)$ whose vertex set is the set of all vertices of~$R$, and whose edges are obtained as follows.
For each rectangle~$r$ of~$R$, we include in~$D(R)$ four edges joining the vertices of~$r$, where the horizontal edges are oriented from left to right, and the vertical edges are oriented from bottom to top.
Hence, the bottom left corner of~$r$ is its source~$s(r)$, while its top right corner is its target~$t(r)$.
Note that since~$R$ is generic, the sources~$\set{s(r)}{r \in [n]}$ and the targets~$\set{t(r)}{r \in [n]}$ are disjoint.
The \defn{source tree}~$S(R)$ (resp.~\defn{target tree}~$T(R)$) is the subgraph of~$D(R)$ induced by the sources~$\set{s(r)}{r \in [n]}$ (resp.~by the targets~$\set{t(r)}{r \in [n]}$).
It is not difficult to check that the source tree~$S(R)$ (resp.~target tree~$T(R)$) is a binary tree, rooted at the bottom left (resp.~top right) corner of~$R$, and oriented from (resp.~towards) its root.

@@

\begin{theorem}
  \label{thm:weakRectangulotope}
  % Jean: I chose to denote the *abstract* polytope by WRP(n), hence changed the next sentence accordingly.
%The weak rectangulotope is realized by the polytope~$\WRP (n) \subset \R^n\!$ defined equivalently~as
The weak rectangulotope $\WRP (n)$ is realized by:
  \begin{enumerate}[(i)]
  \item the convex hull of the points
    \[
    \sum_{i\in [n]} (\loday{w}^R_i - \antiloday{w}^R_i)\cdot \b{e}_i
    \]
    for all weak rectangulations $R$ of size~$n$, with
  \[
    \loday{w}^R_i \eqdef h^T_i\cdot v^T_i
    \qquad\text{and}\qquad
    \antiloday{w}^R_i \eqdef h^S_i\cdot v^S_i,
  \]
  where~$S$ and~$T$ are the source and target trees of the rectangulation~$R$, and $h^T_i$ and $v^T_i$ denote the number of leaves in the horizontal and vertical subtrees of $i$ in~$T$,
\item the intersection of the hyperplane defined by~$\sum_{i \in [n]} x_i = 0$ with the halfspaces defined by
  \[
  \sum_{i \in S} x_i \le \#\set{I \text{ interval of } [n]}{I \not\subseteq S \text{ and } I \not\subseteq [n] \ssm S}
  \]
  for all subsets~$\varnothing \ne S \subsetneq [n]$.
  \end{enumerate}
\end{theorem}

\begin{example}
The weak rectangulotope~$\WRP(4)$ is illustrated in \cref{fig:weakRectangulotope}.
The coordinates of the vertex corresponding to each weak rectangulation are gathered in \cref{tab:verticesWeakRectangulotope}.
The facet inequalities corresponding to each nonempty proper subset of~$[n]$ are gathered in \cref{tab:facetsWeakRectangulotope}.

\begin{table}[p]
	\centerline{
	\begin{tabular}{cccccc}
		\includegraphics[scale=1.5]{rectangulation1} &
		\includegraphics[scale=1.5]{rectangulation2} &
		\includegraphics[scale=1.5]{rectangulation3} &
		\includegraphics[scale=1.5]{rectangulation4} &
		\includegraphics[scale=1.5]{rectangulation5} &
		\includegraphics[scale=1.5]{rectangulation6}
		\\
		$(-3, -1, 1, 3)$ &
		$(-3, -1, 5, -1)$ &
		$(-3, 3, -3, 3)$ &
		$(1, -5, 1, 3)$ &
		$(-3, 0, 5, -2)$ &
		$(-3, 5, -3, 1)$
		\\[.2cm]
		\includegraphics[scale=1.5]{rectangulation8} &
		\includegraphics[scale=1.5]{rectangulation9} &
		\includegraphics[scale=1.5]{rectangulation10} &
		\includegraphics[scale=1.5]{rectangulation11} &
		\includegraphics[scale=1.5]{rectangulation12} &
		\includegraphics[scale=1.5]{rectangulation13}
		\\
		$(-1, 3, -5, 3)$ &
		$(2, -5, 0, 3)$ &
		$(-3, 5, 0, -2)$ &
		$(-2, 0, 5, -3)$ &
		$(1, -5, 5, -1)$ &
		$(-1, 5, -5, 1)$
		\\[.2cm]
		\includegraphics[scale=1.5]{rectangulation14} &
		\includegraphics[scale=1.5]{rectangulation15} &
		\includegraphics[scale=1.5]{rectangulation16} &
		\includegraphics[scale=1.5]{rectangulation17} &
		\includegraphics[scale=1.5]{rectangulation19} &
		\includegraphics[scale=1.5]{rectangulation20}
		\\
		$(3, -5, 0, 2)$ &
		$(2, 0, -5, 3)$ &
		$(-2, 5, 0, -3)$ &
		$(1, -3, 5, -3)$ &
		$(3, -5, 3, -1)$ &
		$(3, 0, -5, 2)$
		\\[.2cm]
		&		
		\includegraphics[scale=1.5]{rectangulation21} &
		\includegraphics[scale=1.5]{rectangulation22} &
		\includegraphics[scale=1.5]{rectangulation23} &
		\includegraphics[scale=1.5]{rectangulation24} &
		\\
		&
		$(-1, 5, -1, -3)$ &
		$(3, -3, 3, -3)$ &
		$(3, 1, -5, 1)$ &
		$(3, 1, -1, -3)$ &
	\end{tabular}
	}
	\caption{The vertices of the weak rectangulotope~$\WRP(4)$ of \cref{fig:weakRectangulotope}.}
	\label{tab:verticesWeakRectangulotope}
\end{table}

@@

\begin{example}
The strong rectangulotope~$\SRP(4)$ is illustrated in \cref{fig:strongRectangulotope}.
The coordinates of the vertex corresponding to each strong rectangulation are gathered in \cref{tab:verticesStrongRectangulotope}.
The facet inequalities corresponding to each nonempty proper subset of~$[n]$ are gathered in \cref{tab:facetsStrongRectangulotope}.

\begin{table}
	\centerline{
	\begin{tabular}{cccccc}
		\includegraphics[scale=1.5]{rectangulation1} &
		\includegraphics[scale=1.5]{rectangulation2} &
		\includegraphics[scale=1.5]{rectangulation3} &
		\includegraphics[scale=1.5]{rectangulation4} &
		\includegraphics[scale=1.5]{rectangulation5} &
		\includegraphics[scale=1.5]{rectangulation6}
		\\
		$(-6, -2, 2, 6)$ &
		$(-6, -2, 9, -1)$ &
		$(-6, 5, -5, 6)$ &
		$(1, -9, 2, 6)$ &
		$(-6, 1, 9, -4)$ &
		$(-6, 9, -5, 2)$
		\\[.2cm]
		\includegraphics[scale=1.5]{rectangulation8} &
		\includegraphics[scale=1.5]{rectangulation9} &
		\includegraphics[scale=1.5]{rectangulation10} &
		\includegraphics[scale=1.5]{rectangulation11} &
		\includegraphics[scale=1.5]{rectangulation12} &
		\includegraphics[scale=1.5]{rectangulation13}
		\\
		$(-2, 5, -9, 6)$ &
		$(4, -9, -1, 6)$ &
		$(-6, 9, 1, -4)$ &
		$(-4, 1, 9, -6)$ &
		$(2, -9, 9, -2)$ &
		$(-2, 9, -9, 2)$
		\\[.2cm]
		\includegraphics[scale=1.5]{rectangulation14} &
		\includegraphics[scale=1.5]{rectangulation15} &
		\includegraphics[scale=1.5]{rectangulation16} &
		\includegraphics[scale=1.5]{rectangulation17} &
		\includegraphics[scale=1.5]{rectangulation19} &
		\includegraphics[scale=1.5]{rectangulation20}
		\\
		$(6, -9, -1, 4)$ &
		$(4, -1, -9, 6)$ &
		$(-4, 9, 1, -6)$ &
		$(2, -5, 9, -6)$ &
		$(6, -9, 5, -2)$ &
		$(6, -1, -9, 4)$
		\\[.2cm]
		\includegraphics[scale=1.5]{rectangulation21} &
		\includegraphics[scale=1.5]{rectangulation22} &
		\includegraphics[scale=1.5]{rectangulation23} &
		\includegraphics[scale=1.5]{rectangulation24} &
		\includegraphics[scale=1.5]{rectangulation7} &
		\includegraphics[scale=1.5]{rectangulation18}
		\\
		$(-1, 9, -2, -6)$ &
		$(6, -5, 5, -6)$ &
		$(6, 2, -9, 1)$ &
		$(6, 2, -2, -6)$ &
		$(1, -9, 9, -1)$ &
		$(-1, 9, -9, 1)$
	\end{tabular}
	}
	\caption{The vertices of the strong rectangulotope~$\SRP(4)$ of \cref{fig:strongRectangulotope}.}
	\label{tab:verticesStrongRectangulotope}
\end{table}

@@

We now briefly recall some results on the weak Bruhat order and its quotients, both from a lattice and geometric perspectives.
We refer to \cite{Reading-arcDiagrams, MR3645055, MR3645056, MR4584712} for details.
% J: Reading-Chapters: which one is this ?

\begin{figure}
	\capstart
	\centerline{\includegraphics[scale=.6]{weakOrderLeft4} \; \includegraphics[scale=.6]{weakOrderCongruence4} \; \includegraphics[scale=.48]{TamariLattice4}}
	\caption{The weak Bruhat order on~$\f{S}_4$ (left), the sylvester congruence~$\equiv_\textrm{sylv}$~(middle), and the Tamari lattice (right). \cite[Fig.~1 \& 2]{MR3964495}}
	\label{fig:sylvesterCongruence}
\end{figure}

@@

@@

%Moreover, the sets of arcs of the form~$\c{A}_\equiv$ are easily described.
\vspace{-.1cm}
\parpic(5cm,2.8cm)(10pt, 90pt)[r][b]{\includegraphics[scale=.5]{subarcOrder}}{
An arc~$(a, b, A, B)$ is a \defn{subarc} of an arc~$(a', b', A', B')$ if \linebreak $a' \le a < b \le b$ and~$A \subseteq A'$ while~$B \subseteq B'$.
An \defn{arc ideal} is a subset of arcs closed by subarcs.
The map~${\equiv} \mapsto \c{A}_\equiv$ is a bijection between the lattice congruences of the weak Bruhat order and the arc ideals.
In other words, the lattice of congruences of the weak Bruhat order is distributive, and its poset of join irreducibles is isomorphic to the subarc order, illustrated on the right for~$n = 4$.
}

@@

\begin{figure}[b]
	\capstart
	\centerline{\includegraphics[scale=.6]{braidFanLeft4} \qquad \raisebox{-.3cm}{\includegraphics[scale=.6]{sylvesterFan4}}}
	\caption{The braid fan (left) and the sylvester fan (right). \cite[Fig.~1]{MR3964495} \&~\cite[Fig.~5]{MR4584712}}
	\label{fig:fans}
\end{figure}

@@

Consider an arc~$\alpha \eqdef (a, b, A, B)$ on~$[n]$.
An \defn{$\alpha$-alternating matching} is a sequence~$a \le i_1 < j_1 < i_2 < j_2 < \dots < i_q < j_q \le b$ such that~$i_p \in \{a\} \cup A$ and~$j_p \in \{b\} \cup B$ for all~$p \in [q]$.
Its \defn{characteristic vector} is~$\sum_{p \in [q]} \b{e}_{i_p} - \b{e}_{j_p}$.
The \defn{shard polytope} of~$\alpha$ is the convex hull~$\SP(\alpha)$ of the characteristic vectors of all $\alpha$-alternating matchings.
We refer to Figure~\ref{fig:shardPolytopes} for an illustration of this definition.
It was shown in~\cite{MR4584712} that any Minkowski sum of positive scalings of the shard polytopes~$\SP(\alpha)$ for all arcs~$\alpha$ in the arc ideal~$\c{A}_\equiv$ is a quotientope for~$\equiv$.

@@

\section{Weak rectangulotopes}
\label{sec:weakRectangulotopes}

%%%%%%%%%%%%%
\subsection{The weak poset}
\label{subsec:weakPoset}

@@

%%%%%%%%%%%%%
\subsection{The weak rectangulation congruence}
\label{subsec:weakRectangulationCongruence}

@@

We recall that \emph{Baxter permutations} are permutations avoiding the vincular pattern $2\underline{41}3$ and $3\underline{14}2$, where the underlining indicates that the symbols must appear contiguously in the permutation.
Similarly, \defn{twisted Baxter permutations} are permutations avoiding the patterns $2\underline{41}3$ and $3\underline{41}2$, and \defn{co-twisted Baxter permutations} are permutations avoiding the patterns $2\underline{14}3$ and $3\underline{14}2$.
These permutation families are central in the theory of rectangulations and appear in many other contexts~\cite{MR2763051}.

>>>>

\begin{figure}
	\capstart
	\centerline{\includegraphics[scale=.75]{permutahedronLeft4} \quad \raisebox{-.4cm}{\includegraphics[scale=.75]{associahedron4}}}
	\caption{The permutahedron~$\Perm(4)$ (left) and the associahedron~$\Asso(4)$ (right). \cite[Fig.~1]{MR3964495} \&~\cite[Fig.~5]{MR4584712}}
	\label{fig:quotientopes}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=.9\textwidth]{rectangulations.pdf}
	\caption{Three rectangulations. All three rectangulations are weakly equivalent, but only the first two are strongly equivalent. Only the third one is diagonal.}
	\label{fig:rectequiv}
\end{figure}
\vincent{Add one which is not weakly equivalent?}

@@

\begin{figure}
	\centerline{\includegraphics[width=.4\textwidth]{strongRectangulation} \qquad \includegraphics[width=.4\textwidth]{strongRectangulationTrees}}
	\caption{A rectangulation $R$ (left) and its pair of binary trees $S(R)$ and $T(R)$ (right). Example from \cite{ACFF24}.}
        % The corresponding $2$-clumped permutation is $[7,5,14,8,1,6,15,11,4,10,16,2,9,13,3,12]$ and its inverse is $[5, 12, 15, 9, 2, 6, 1, 4, 13, 10, 8, 16, 14, 3, 7, 11]$.
        \label{fig:strongRectangulation}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=.4\textwidth]{weakRectangulation} \qquad \includegraphics[width=.4\textwidth]{weakRectangulationTrees}}
	\caption{A diagonal rectangulation (left) and its pair of twin binary trees (right). Example from \cite{ACFF24}.}
	% The corresponding twisted Baxter permutation is $[7, 5, 1, 14, 8, 6, 4, 2, 11, 10, 9, 3, 15, 16, 13, 12]$ and its inverse is $[3, 8, 12, 7, 2, 6, 1, 5, 11, 10, 9, 16, 15, 4, 13, 14]$.
	\label{fig:weakRectangulation}
\end{figure}

@@

Fix a rectangulation~$R$ of size~$n$, and consider the directed graph~$D(R)$ whose vertex set is the set of all vertices of~$R$, and whose edges are obtained as follows.
For each rectangle~$r$ of~$R$, we include in~$D(R)$ four edges joining the vertices of~$r$, where the horizontal edges are oriented from left to right, and the vertical edges are oriented from bottom to top.
Hence, the bottom left corner of~$r$ is its source~$s(r)$, while its top right corner is its target~$t(r)$.
Note that since~$R$ is generic, the sources~$\set{s(r)}{r \in R}$ and the targets~$\set{t(r)}{r \in R}$ are disjoint.
The \defn{source tree}~$S(R)$ (resp.~\defn{target tree}~$T(R)$) is the subgraph of~$D(R)$ induced by the sources~$\set{s(r)}{r \in R}$ (resp.~by the targets~$\set{t(r)}{r \in R}$).
It is not difficult to check that the source tree~$S(R)$ (resp.~target tree~$T(R)$) is a binary tree, rooted at the bottom left (resp.~top right) corner of~$R$, and oriented from (resp.~towards) its root.

@@

\begin{theorem}
  \label{thm:weakRectangulotope}
  % Jean: I chose to denote the *abstract* polytope by WRP(n), hence changed the next sentence accordingly.
%The weak rectangulotope is realized by the polytope~$\WRP (n) \subset \R^n\!$ defined equivalently~as
The weak rectangulotope $\WRP (n)$ is realized by: \vincent{We loose the information that the two descriptions define the same polytope...}
  \begin{enumerate}[(i)]
  \item the convex hull of the points
    \[
    \sum_{i\in [n]} (\loday{w}^R_i - \antiloday{w}^R_i)\cdot \b{e}_i
    \]
    for all weak rectangulations $R$ of size~$n$, with
  \[
    \loday{w}^R_i \eqdef h^T_i\cdot v^T_i
    \qquad\text{and}\qquad
    \antiloday{w}^R_i \eqdef h^S_i\cdot v^S_i,
  \]
  where~$S$ and~$T$ are the source and target trees of the rectangulation~$R$, and $h^T_i$ and $v^T_i$ denote the number of leaves in the horizontal and vertical subtrees of $i$ in~$T$,
\item the intersection of the hyperplane defined by~$\sum_{i \in [n]} x_i = 0$ with the halfspaces defined by
  \[
  \sum_{i \in S} x_i \le \#\set{I \text{ interval of } [n]}{I \not\subseteq S \text{ and } I \not\subseteq [n] \ssm S}
  \]
  for all subsets~$\varnothing \ne S \subsetneq [n]$.
  \end{enumerate}
\end{theorem}

\begin{table}
	\centerline{
	\begin{tabular}{cccccc}
		\includegraphics[scale=2]{rectangulation1} &
		\includegraphics[scale=2]{rectangulation2} &
		\includegraphics[scale=2]{rectangulation3} &
		\includegraphics[scale=2]{rectangulation4} &
		\includegraphics[scale=2]{rectangulation5} &
		\includegraphics[scale=2]{rectangulation6}
		\\[-.1cm]
		$(-3, -1, 1, 3)$ &
		$(-3, -1, 5, -1)$ &
		$(-3, 3, -3, 3)$ &
		$(1, -5, 1, 3)$ &
		$(-3, 0, 5, -2)$ &
		$(-3, 5, -3, 1)$
		\\[.2cm]
		\includegraphics[scale=2]{rectangulation8} &
		\includegraphics[scale=2]{rectangulation9} &
		\includegraphics[scale=2]{rectangulation10} &
		\includegraphics[scale=2]{rectangulation11} &
		\includegraphics[scale=2]{rectangulation12} &
		\includegraphics[scale=2]{rectangulation13}
		\\[-.1cm]
		$(-1, 3, -5, 3)$ &
		$(2, -5, 0, 3)$ &
		$(-3, 5, 0, -2)$ &
		$(-2, 0, 5, -3)$ &
		$(1, -5, 5, -1)$ &
		$(-1, 5, -5, 1)$
		\\[.2cm]
		\includegraphics[scale=2]{rectangulation14} &
		\includegraphics[scale=2]{rectangulation15} &
		\includegraphics[scale=2]{rectangulation16} &
		\includegraphics[scale=2]{rectangulation17} &
		\includegraphics[scale=2]{rectangulation19} &
		\includegraphics[scale=2]{rectangulation20}
		\\[-.1cm]
		$(3, -5, 0, 2)$ &
		$(2, 0, -5, 3)$ &
		$(-2, 5, 0, -3)$ &
		$(1, -3, 5, -3)$ &
		$(3, -5, 3, -1)$ &
		$(3, 0, -5, 2)$
		\\[.2cm]
		&		
		\includegraphics[scale=2]{rectangulation21} &
		\includegraphics[scale=2]{rectangulation22} &
		\includegraphics[scale=2]{rectangulation23} &
		\includegraphics[scale=2]{rectangulation24} &
		\\[-.1cm]
		&
		$(-1, 5, -1, -3)$ &
		$(3, -3, 3, -3)$ &
		$(3, 1, -5, 1)$ &
		$(3, 1, -1, -3)$ &
	\end{tabular}
	}
	\caption{The vertices of the weak rectangulotope~$\WRP(4)$ of \cref{fig:weakRectangulotope}.}
	\label{tab:verticesWeakRectangulotope}
\end{table}

\begin{table}
	\centerline{
	\begin{tabular}{cccccc}
		\includegraphics[scale=2]{rectangulation1} &
		\includegraphics[scale=2]{rectangulation2} &
		\includegraphics[scale=2]{rectangulation3} &
		\includegraphics[scale=2]{rectangulation4} &
		\includegraphics[scale=2]{rectangulation5} &
		\includegraphics[scale=2]{rectangulation6}
		\\[-.1cm]
		$(-6, -2, 2, 6)$ &
		$(-6, -2, 9, -1)$ &
		$(-6, 5, -5, 6)$ &
		$(1, -9, 2, 6)$ &
		$(-6, 1, 9, -4)$ &
		$(-6, 9, -5, 2)$
		\\[.2cm]
		\includegraphics[scale=2]{rectangulation8} &
		\includegraphics[scale=2]{rectangulation9} &
		\includegraphics[scale=2]{rectangulation10} &
		\includegraphics[scale=2]{rectangulation11} &
		\includegraphics[scale=2]{rectangulation12} &
		\includegraphics[scale=2]{rectangulation13}
		\\[-.1cm]
		$(-2, 5, -9, 6)$ &
		$(4, -9, -1, 6)$ &
		$(-6, 9, 1, -4)$ &
		$(-4, 1, 9, -6)$ &
		$(2, -9, 9, -2)$ &
		$(-2, 9, -9, 2)$
		\\[.2cm]
		\includegraphics[scale=2]{rectangulation14} &
		\includegraphics[scale=2]{rectangulation15} &
		\includegraphics[scale=2]{rectangulation16} &
		\includegraphics[scale=2]{rectangulation17} &
		\includegraphics[scale=2]{rectangulation19} &
		\includegraphics[scale=2]{rectangulation20}
		\\[-.1cm]
		$(6, -9, -1, 4)$ &
		$(4, -1, -9, 6)$ &
		$(-4, 9, 1, -6)$ &
		$(2, -5, 9, -6)$ &
		$(6, -9, 5, -2)$ &
		$(6, -1, -9, 4)$
		\\[.2cm]
		\includegraphics[scale=2]{rectangulation21} &
		\includegraphics[scale=2]{rectangulation22} &
		\includegraphics[scale=2]{rectangulation23} &
		\includegraphics[scale=2]{rectangulation24} &
		\includegraphics[scale=2]{rectangulation7} &
		\includegraphics[scale=2]{rectangulation18}
		\\[-.1cm]
		$(-1, 9, -2, -6)$ &
		$(6, -5, 5, -6)$ &
		$(6, 2, -9, 1)$ &
		$(6, 2, -2, -6)$ &
		$(1, -9, 9, -1)$ &
		$(-1, 9, -9, 1)$
	\end{tabular}
	}
	\caption{The vertices of the strong rectangulotope~$\SRP(4)$ of \cref{fig:strongRectangulotope}.}
	\label{tab:verticesStrongRectangulotope}
\end{table}

\begin{example}
The weak rectangulotope~$\WRP(4)$ is illustrated in \cref{fig:weakRectangulotope}.
The coordinates of the vertices corresponding to all weak rectangulations are gathered in \cref{tab:verticesWeakRectangulotope}.
The facet inequalities corresponding to each nonempty proper subset of~$[n]$ are gathered in \cref{tab:facetsWeakRectangulotope}.

%\begin{table}[p]
%	\centerline{
%	\begin{tabular}{cccccc}
%		\includegraphics[scale=1.5]{rectangulation1} &
%		\includegraphics[scale=1.5]{rectangulation2} &
%		\includegraphics[scale=1.5]{rectangulation3} &
%		\includegraphics[scale=1.5]{rectangulation4} &
%		\includegraphics[scale=1.5]{rectangulation5} &
%		\includegraphics[scale=1.5]{rectangulation6}
%		\\
%		$(-3, -1, 1, 3)$ &
%		$(-3, -1, 5, -1)$ &
%		$(-3, 3, -3, 3)$ &
%		$(1, -5, 1, 3)$ &
%		$(-3, 0, 5, -2)$ &
%		$(-3, 5, -3, 1)$
%		\\[.2cm]
%		\includegraphics[scale=1.5]{rectangulation8} &
%		\includegraphics[scale=1.5]{rectangulation9} &
%		\includegraphics[scale=1.5]{rectangulation10} &
%		\includegraphics[scale=1.5]{rectangulation11} &
%		\includegraphics[scale=1.5]{rectangulation12} &
%		\includegraphics[scale=1.5]{rectangulation13}
%		\\
%		$(-1, 3, -5, 3)$ &
%		$(2, -5, 0, 3)$ &
%		$(-3, 5, 0, -2)$ &
%		$(-2, 0, 5, -3)$ &
%		$(1, -5, 5, -1)$ &
%		$(-1, 5, -5, 1)$
%		\\[.2cm]
%		\includegraphics[scale=1.5]{rectangulation14} &
%		\includegraphics[scale=1.5]{rectangulation15} &
%		\includegraphics[scale=1.5]{rectangulation16} &
%		\includegraphics[scale=1.5]{rectangulation17} &
%		\includegraphics[scale=1.5]{rectangulation19} &
%		\includegraphics[scale=1.5]{rectangulation20}
%		\\
%		$(3, -5, 0, 2)$ &
%		$(2, 0, -5, 3)$ &
%		$(-2, 5, 0, -3)$ &
%		$(1, -3, 5, -3)$ &
%		$(3, -5, 3, -1)$ &
%		$(3, 0, -5, 2)$
%		\\[.2cm]
%		&		
%		\includegraphics[scale=1.5]{rectangulation21} &
%		\includegraphics[scale=1.5]{rectangulation22} &
%		\includegraphics[scale=1.5]{rectangulation23} &
%		\includegraphics[scale=1.5]{rectangulation24} &
%		\\
%		&
%		$(-1, 5, -1, -3)$ &
%		$(3, -3, 3, -3)$ &
%		$(3, 1, -5, 1)$ &
%		$(3, 1, -1, -3)$ &
%	\end{tabular}
%	}
%	\caption{The vertices of the weak rectangulotope~$\WRP(4)$ of \cref{fig:weakRectangulotope}.}
%	\label{tab:verticesWeakRectangulotope}
%\end{table}

@@

\begin{example}
The strong rectangulotope~$\SRP(4)$ is illustrated in \cref{fig:strongRectangulotope}.
The coordinates of the vertices corresponding to all strong rectangulations are gathered in \cref{tab:verticesStrongRectangulotope}.
The facet inequalities corresponding to each nonempty proper subset of~$[n]$ are gathered in \cref{tab:facetsStrongRectangulotope}.

%\begin{table}
%	\centerline{
%	\begin{tabular}{cccccc}
%		\includegraphics[scale=1.5]{rectangulation1} &
%		\includegraphics[scale=1.5]{rectangulation2} &
%		\includegraphics[scale=1.5]{rectangulation3} &
%		\includegraphics[scale=1.5]{rectangulation4} &
%		\includegraphics[scale=1.5]{rectangulation5} &
%		\includegraphics[scale=1.5]{rectangulation6}
%		\\
%		$(-6, -2, 2, 6)$ &
%		$(-6, -2, 9, -1)$ &
%		$(-6, 5, -5, 6)$ &
%		$(1, -9, 2, 6)$ &
%		$(-6, 1, 9, -4)$ &
%		$(-6, 9, -5, 2)$
%		\\[.2cm]
%		\includegraphics[scale=1.5]{rectangulation8} &
%		\includegraphics[scale=1.5]{rectangulation9} &
%		\includegraphics[scale=1.5]{rectangulation10} &
%		\includegraphics[scale=1.5]{rectangulation11} &
%		\includegraphics[scale=1.5]{rectangulation12} &
%		\includegraphics[scale=1.5]{rectangulation13}
%		\\
%		$(-2, 5, -9, 6)$ &
%		$(4, -9, -1, 6)$ &
%		$(-6, 9, 1, -4)$ &
%		$(-4, 1, 9, -6)$ &
%		$(2, -9, 9, -2)$ &
%		$(-2, 9, -9, 2)$
%		\\[.2cm]
%		\includegraphics[scale=1.5]{rectangulation14} &
%		\includegraphics[scale=1.5]{rectangulation15} &
%		\includegraphics[scale=1.5]{rectangulation16} &
%		\includegraphics[scale=1.5]{rectangulation17} &
%		\includegraphics[scale=1.5]{rectangulation19} &
%		\includegraphics[scale=1.5]{rectangulation20}
%		\\
%		$(6, -9, -1, 4)$ &
%		$(4, -1, -9, 6)$ &
%		$(-4, 9, 1, -6)$ &
%		$(2, -5, 9, -6)$ &
%		$(6, -9, 5, -2)$ &
%		$(6, -1, -9, 4)$
%		\\[.2cm]
%		\includegraphics[scale=1.5]{rectangulation21} &
%		\includegraphics[scale=1.5]{rectangulation22} &
%		\includegraphics[scale=1.5]{rectangulation23} &
%		\includegraphics[scale=1.5]{rectangulation24} &
%		\includegraphics[scale=1.5]{rectangulation7} &
%		\includegraphics[scale=1.5]{rectangulation18}
%		\\
%		$(-1, 9, -2, -6)$ &
%		$(6, -5, 5, -6)$ &
%		$(6, 2, -9, 1)$ &
%		$(6, 2, -2, -6)$ &
%		$(1, -9, 9, -1)$ &
%		$(-1, 9, -9, 1)$
%	\end{tabular}
%	}
%	\caption{The vertices of the strong rectangulotope~$\SRP(4)$ of \cref{fig:strongRectangulotope}.}
%	\label{tab:verticesStrongRectangulotope}
%\end{table}

@@

We now briefly recall some results on the weak Bruhat order and its quotients, both from a lattice and geometric perspectives.
We refer to \cite{MR2142177, Reading-arcDiagrams, MR3645055, MR3645056, MR3964495, MR4584712} for details.
% J: Reading-Chapters: which one is this ?

@@

\afterpage{
\begin{figure}
	\capstart
	\centerline{\includegraphics[scale=.6]{weakOrderLeft4} \; \includegraphics[scale=.6]{weakOrderCongruence4} \; \includegraphics[scale=.48]{TamariLattice4}}
	\caption{The weak Bruhat order on~$\f{S}_4$ (left), the sylvester congruence~$\equiv_\textrm{sylv}$~(middle), and the Tamari lattice (right). \cite[Fig.~1 \& 2]{MR3964495}}
	\label{fig:sylvesterCongruence}
\end{figure}
}

@@

%Moreover, the sets of arcs of the form~$\c{A}_\equiv$ are easily described.
\vspace{-.2cm}
\parpic(5cm,2.8cm)(10pt, 90pt)[r][b]{\includegraphics[scale=.5]{subarcOrder}}{
An arc~$(a, b, A, B)$ is a \defn{subarc} of an arc~$(a', b', A', B')$ if \linebreak $a' \le a < b \le b$ and~$A \subseteq A'$ while~$B \subseteq B'$.
An \defn{arc ideal} is a subset of arcs closed by subarcs.
The map~${\equiv} \mapsto \c{A}_\equiv$ is a bijection between the lattice congruences of the weak Bruhat order and the arc ideals.
In other words, the lattice of congruences of the weak Bruhat order is distributive, and its poset of join irreducibles is isomorphic to the subarc order, illustrated on the right for~$n = 4$.
}

@@

\begin{figure}[b]
	\capstart
	\centerline{\includegraphics[scale=.75]{braidFanLeft4} \quad \raisebox{-.3cm}{\includegraphics[scale=.75]{sylvesterFan4}}}
	\caption{The braid fan (left) and the sylvester fan (right). \cite[Fig.~1]{MR3964495} \&~\cite[Fig.~5]{MR4584712}}
	\label{fig:fans}
\end{figure}

@@

Consider an arc~$\alpha \eqdef (a, b, A, B)$ on~$[n]$.
An \defn{$\alpha$-alternating matching} is a sequence~$a \le i_1 < j_1 < i_2 < j_2 < \dots < i_q < j_q \le b$ such that~$i_p \in \{a\} \cup A$ and~$j_p \in \{b\} \cup B$ for all~$p \in [q]$.
Its \defn{characteristic vector} is~$\sum_{p \in [q]} \b{e}_{i_p} - \b{e}_{j_p}$.
The \defn{shard polytope} of~$\alpha$ is the convex hull~$\SP(\alpha)$ of the characteristic vectors of all $\alpha$-alternating matchings.
We refer to \cref{fig:shardPolytopes} for an illustration of this definition.
It was shown in~\cite{MR4584712} that any Minkowski sum of positive scalings of the shard polytopes~$\SP(\alpha)$ for all arcs~$\alpha$ in the arc ideal~$\c{A}_\equiv$ is a quotientope for~$\equiv$.

@@

\pagebreak
\section{Weak rectangulotopes}
\label{sec:weakRectangulotopes}

This section is devoted to weak rectangulations and the proof of \cref{thm:weakRectangulotope}.

\subsection{The weak poset}
\label{subsec:weakPoset}

@@

\subsection{The weak rectangulation congruence}
\label{subsec:weakRectangulationCongruence}

@@

We recall that \emph{Baxter permutations} are permutations avoiding the vincular patterns $2\underline{41}3$ and $3\underline{14}2$, where the underlining indicates that the symbols must appear contiguously in the permutation.
Similarly, \defn{twisted Baxter permutations} are permutations avoiding the patterns $2\underline{41}3$ and $3\underline{41}2$, and \defn{co-twisted Baxter permutations} are permutations avoiding the patterns $2\underline{14}3$ and $3\underline{14}2$.
These permutation families are central in the theory of rectangulations and appear in many other contexts~\cite{MR2763051}.
